%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{comment}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust
%the width of the space allocated to your name

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Gennaro}
\familyname{Tedesco}

\title{Curriculum Vitae}
%\address{Am Postbahnhof, 21}{10243 Berlin, Germany}
\mobile{+491796452983}
\email{gennarotedesco@gmail.com}
\homepage{https://github.com/gennaro-tedesco}{https://github.com/gennaro-tedesco}
%\photo[100pt][0.4pt]{pictures/photo}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Current Position} 2023--present: \textbf{Team lead artificial and document
	intelligence} at Finlink, Berlin.

\bigskip Responsible of a team of engineers and researchers implementing and
integrating machine learning models and document intelligence into our
software. We bring document classification and information extraction to our
document platform and build software for banks and independent
advisors to use. My role as manager is to ensure that company objectives are
efficiently translated into our software, as well as to supervise the entire
development and infrastructure process.

\section{Experience}
\cventry[8pt]{2021--2023}{Tech lead data science}{}{Billie, Berlin}{}{%
	Team lead supervising development of machine learning services in payment and
	identification domain: payment validation, identification of suspicious
	buyers and credit risk. My role was to
	direct the entire development process, from the initial business requirements
	through the scientific phase of model development until service integration in
	our platform.}

\cventry[8pt]{2019--2021}{Senior data scientist}{}{Billie, Berlin}{}{%
	Introduction and development of the entire area of NLP in the financial domain to assess risk and detect fraud. Language model classification with general deep learning algorithms on structured text; time series analyses in the financial domain and test of hypotheses for statistical significance. Development and deployment of (internal) applications for business intelligence. }

\cventry[8pt]{2016--2019}{Data scientist}{}{Leverton, Berlin}{}{%
	Development of deep learning models in NLP with corresponding classification
	algorithms. Implementation of predictive models, time series analyses and
	hypotheses tests. Development of internal applications for business intelligence.}

\cventry[8pt]{2015--2016}{Data scientist}{}{HelloFresh, Berlin}{} {%
	Development of prediction and forecasting models for customers churns and acquisitions. Study of time series behaviours, network analyses, implementation of machine learning algorithms for classification and regression.}

\cventry[8pt]{2014--2015}{Data Analyst}{}{Bank of America Merrill Lynch, London}{}{}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\newpage
\section{Academic Education}

\cventry[8pt]{2011--2014}{PhD in theoretical
	physics}{}{Georg August University of G\"ottingen, magna cum laude. PhD thesis
	\textit{``Modular structure of chiral Fermi fields in low dimensional conformal
		field theory''}}{}{}

\cventry[8pt]{2005--2011}{Master degree in theoretical
	physics}{}{University of Naples} {110/110 cum laude. Thesis \textit{``Discrete quantum
		field theory of the gravitational field''}}{}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{Projects:}

\cvlistitem{Author of several neovim plugins and command line applications}
\cvlistitem{Active contributor to neovim and other open-source projects and libraries}
\cvlistitem{Invited speaker for podcasts and meetups}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer languages}
\cvitem{Languages}{Python, R, Go, Lua, SQL, bash, awk, \LaTeX, Rust}
\cvitem{Infrastructure}{docker, kubernetes, dvc, AWS, Azure}
\cvitem{cli}{jq, visidata, sed, awk, GNU core utils}
\cvitem{BI}{Tableau, Sisense}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}
\cvitemwithcomment{Italian}{Mother tongue}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{German}{Very good}{}
\cvitemwithcomment{Chinese}{Beginner}{}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}

\cvlistitem{G. Tedesco: \textit{``Modular structure of
		chiral Fermi fields in conformal quantum field theory''}; eDiss SUB
	G\"ottingen}

\cvlistitem{K. -H. Rehren, G. Tedesco: \textit{``Multilocal
	Fermionization''}; Lett.\ Math.\ Phys.\  {\bfseries{103}} (2013) 19
[arXiv:1205.0324 [math-ph]].}

\subsection{Unpublished material}

\cvlistitem{G. Tedesco: \textit{Introduction to the theory of connections on principal bundles};}

\cvlistitem{G. Tedesco: \textit{Generalised Efron's dice problem: simple solutions};}

\cvlistitem{G. Tedesco: \textit{R for data science};}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}
\cvlistitem{I play basketball and chess in my spare time (less often tennis
	and volleyball)}
\cvlistitem{I played a major role in a short film (available online)
	about cultural exchanges among different countries at high academic level}

\end{document}
